---
title: "My Report"
author: "Kara Woo"
date: "5/29/2019"
output: html_document
---

```{r global_options, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = "figs/")
```


*This is some formatting*

**Some other formatting**

[A hyperlink](https://google.com)

- A bulleted list
- Another list item

1. A numbered list
1. A second numbered item.
   1. sub-item
       1. sub-sub item

```{r load_data}
library("gapminder")
library("ggplot2")
library("tidyverse")
data(gapminder)
head(gapminder)
```

```{r gdp_lifeexp_plot}
ggplot(data = gapminder, mapping = aes(x = gdpPercap, y = lifeExp)) +
  geom_point()
```

```{r lifeexp_over_time, fig.width = 3}
ggplot(data = gapminder, mapping = aes(x = year, y = lifeExp)) +
  geom_point()
```

The largest population of any country in this dataset is `r max(gapminder$pop)`.

```{r iceland, echo = FALSE}
iceland <- filter(gapminder, country == "Iceland")
max_iceland_lifeexp <- max(iceland$lifeExp)
```

The maximum life expectancy in Iceland is `r max_iceland_lifeexp`.

```{r}
gap_1977 <- gapminder %>%
  filter(year == 1977)
gdp_range <- c(min(gap_1977$gdpPercap), max(gap_1977$gdpPercap))
```

The lowest GDP/capita of any country in 1977 was `r gdp_range[1]` and the highest GDP/capita of any country in 1977 was `r gdp_range[2]`.


```
git config --global user.name "Jane Doe"
git config --global user.email "jane@example.com"
git config --global core.editor 'nano'
git init
```

